Baseline centering problem

### 2018-12-19 paper/tangotd.tex

\paragraph{Variant.}
I think
everything works equally well if we just learn a kernel $Z(s_1,s_2)$ such
that
\begin{equation}
\transp{\1_{s_1}}\Delta^{-1}\psi\approx \E_{s_2\sim \rho} Z(s_1,s_2)
\psi(s_2)
\end{equation}
and this is still linear in $\psi$. This represents the inverse Laplace
operator by
\begin{equation}
Z=\sum_{s_1,s_2}\rho(s_2)  Z(s_1,s_2)\1_{s_1}\transp{\1_{s_2}}
\end{equation}
and in particular the value function is
\begin{equation}
V(s_1)=\E_{s_2\sim \rho} Z(s_1,s_2) R(s_2)
\end{equation}
This representation of the value function does not allow for first
computing $\E_{s_2} R(s_2)f(s_2)$ online, then taking a dot product with
$\green$. Here we would have to learn an auxiliary network to imitate
$\E_{s_2\sim \rho} Z(s_1,s_2) R(s_2)$ (but this is a supervised learning
problem). Alternatively, policy gradient can just directly be obtained
via
\begin{equation}
\partial \pi(a|s)\E_{s'|s,a} \E_{s_2\sim \rho} Z(s',s_2)R(s_2)
\end{equation}
(this works even if $\rho$ is \emph{not} the invariant distribution).

>>>>

\paragraph{Variant.}
I think
everything works equally well if we just learn a kernel $Z(s_1,s_2)$ such
that
\begin{equation}
\transp{\1_{s_1}}\Delta^{-1}\psi\approx \E_{s_2\sim \rho} Z(s_1,s_2)
\psi(s_2)
\end{equation}
and this is still linear in $\psi$. This represents the inverse Laplace
operator by
\begin{equation}
Z=\sum_{s_1,s_2}\rho(s_2)  Z(s_1,s_2)\1_{s_1}\transp{\1_{s_2}}
\end{equation}
In particular the value function is
\begin{equation}
V(s_1)=\E_{s_2\sim \rho} Z(s_1,s_2) R(s_2)
\end{equation}
This representation of the value function does not allow for first
computing $\E_{s_2} R(s_2)f(s_2)$ online, then taking a dot product with
$\green$. Here we would have to learn an auxiliary network to imitate
$\E_{s_2\sim \rho} Z(s_1,s_2) R(s_2)$ (but this is a supervised learning
problem). Alternatively, policy gradient can just directly be obtained
via
\begin{equation}
\partial \pi(a|s)\E_{s'|s,a} \E_{s_2\sim \rho} Z(s',s_2)R(s_2)
\end{equation}
(this works even if $\rho$ is \emph{not} the invariant distribution). We
can apply this each time a new reward is observed at some point $s_2$. We
can even set another arbitrary distribution on $s_1$: this policy
gradient will maximize
the reward obtained from a starting point from that distribution.
